Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-01 Draft/shower.tex
Update small correction shower.tex

We now turn to discuss how different predictions compare when the matching to parton-shower (PS) is included. For such
a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
matching schemes, PS employed and of the other details of the matching (such as the choice of the shower initial scale). Among
the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, {\sc POWHEG} and {\sc VBFNLO}
can also provide results at (N)LO+PS accuracy. Besides, also {\sc PHANTOM} is employed for LO+PS results.\\
{\sc MG5\_aMC},
which
employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 2.2.3)
and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For {\sc POWHEG}, the omonymous matching procedure is 
employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8}
{\bf MZ VERSION? if same as MG5, put it at the end together with the tune}. {\sc VBFNLO} makes it possible to choose between the {\sc MC@NLO} and {\sc POWHEG}
matching, in both cases together with {\sc Herwig7}~CITEREF. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8}.
Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.\\

Results will be presented within the cuts described in Section~\ref{subsec:inputpar}, applied after shower and hadronization (this implies that jets
are obtained by clustering stable hadrons, and not QCD partons). This implies that at the event-generation level, looser cuts (or no cuts at all)
must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\

@@

The first observable we invesigate is the exclusive jet multiplicity, shown in Figure~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the

@@

Finally, we conclude the list of differential observable with two observables related to the third jet, the rapidity and the $z$ variable, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}. 
{\bf MZ the rapidity can be dropped (check also the following discussion in case); if z is defined elsewhere in the paper, then add a ref to the proper sectiomn. Otherwise define it here} 

>>>>

We now turn to discuss how different predictions compare when the matching to parton-shower (PS) is included. For such
a comparison we expect larger discrepancy than what we found at fixed-order, as a consequence of the different
matching schemes, PS employed and of the other details of the matching (such as the choice of the shower initial scale). Among
the codes capable of providing fixed-order results, presented before, {\sc MG5\_aMC}, {\sc POWHEG} and {\sc VBFNLO}
can also provide results at (N)LO+PS accuracy. Besides, also {\sc PHANTOM} is employed for LO+PS results.\\
{\sc MG5\_aMC},
which
employs the {\sc MC@NLO}~\cite{Frixione:2002ik} matching procedure, will be used together with {\sc Pythia8}~\cite{Sjostrand:2014zea} (version 2.2.3)
and {\sc Herwig++}~\cite{Bahr:2008pv, Bellm:2013hwb} (version 2.7.1). For {\sc POWHEG}, the omonymous matching procedure is 
employed~\cite{Nason:2004rx,Frixione:2007vw}, together with {\sc Pythia8}
{\bf MZ VERSION? if same as MG5, put it at the end together with the tune}. {\sc VBFNLO} makes it possible to choose between the {\sc MC@NLO} and {\sc POWHEG}
matching, in both cases together with {\sc Herwig7}~CITEREF. Finally, {\sc PHANTOM} results will be shown matched with {\sc Pythia 8} and {\sc Herwig++}.
Whenever {\sc Pythia8}\ is used, the Monash tune~\cite{Skands:2014pea} is selected.\\

Results will be presented within the cuts described in Section~\ref{subsec:inputpar}, applied after shower and hadronization (this implies that jets
are obtained by clustering stable hadrons, and not QCD partons). It follows that at the event-generation level, looser cuts (or no cuts at all)
must be employed in order not to bias the results. {\bf MZ lepton-jet separation at the hard-event level?}.\\

@@

The first observable we investigate is the exclusive jet multiplicity, shown in Figure~\ref{fig:PSnjet}. Looking at the LO+PS predictions, one can appreciate that the

@@

Finally, focusing on the third jet, we conclude the list of differential observable with the rapidity and the $z$ variable, Figures~\ref{fig:PSy3} and~\ref{fig:PSz3}. 
{\bf MZ the rapidity can be dropped (check also the following discussion in case); if z is defined elsewhere in the paper, then add a ref to the proper section. Otherwise define it here} 
